Methodology for Assessing the State of the Practice for Domain X

### 2020-08-05 StateOfPractice/Methodology/Methodology.tex
added some points and questions to 'Overview of Steps in Assessing Quality of the Domain Software'

\begin{enumerate}
\item Start with state of practice research questions.
\item Identify domain.  (Provide criteria on a candidate domain.)
\item Identify list of candidate software in the domain.  (Section~\ref{SecIdentifyCandSoft})
\item \emph{Domain Expert}: Vet domain software list.  
\item Domain Analysis. (Section~\ref{SecDomainAnalysis})
\item \emph{Domain Expert}: Vet domain analysis
\item Measure using ``shallow'' measurement template.
\item Empirical measures.
\item Use AHP process to rank the software.  Tool for estimating AHP results?
  Tool for ranking and sorting by various criteria?  Conditional formula to
  assess software within each measure, or just use opinion of measurer?
\item Identify short list for deeper exploration.
\item \emph{Domain Expert}: vet AHP ranking and short list.
\item With short list:
\begin{enumerate}
\item Survey developers
\item Usability experiments
\item Performance benchmarks
\item Maintainability experiments
\end{enumerate}
\item Compare shallow and deep measures and ranking
\item Answers for research questions.
\end{enumerate}

@@

\begin{enumerate}
\item Must be open source.
\item Must have GitHub repository.
\end{enumerate}

>>>>

\begin{enumerate}
\item Start with state of practice research questions.
\item Identify domain.  (Provide criteria on a candidate domain.)
\item Identify list of candidate software in the domain. \pmi{Do we want to outline how to find such a list?} (Section~\ref{SecIdentifyCandSoft})
\item Filter domain software list. (Judge on professionalism, available documentation, status, availability of source code) \pmi{The original document lists the Domain Expert as responsible for this. Should we have had them vet the list prior to taking our measurements?}
\item Domain Analysis. (Section~\ref{SecDomainAnalysis})
\item \emph{Domain Expert}: Vet domain analysis.
\item Gather source code and documentation.
\item Empirical measures.
\item Measure using ``shallow'' measurement template. \pmi{Do we want to comment on the creation of this template and why certain qualities were chosen?}
\item Use AHP process to rank the software.  Tool for estimating AHP results?
  Tool for ranking and sorting by various criteria?  Conditional formula to
  assess software within each measure, or just use opinion of measurer? \pmi{Will we want to rank the qualities before we implement AHP? Will we provide our AHP tool?}
\item Decide on desired short list size.  
\item Identify short list for deeper exploration using AHP rankings of shallow measurements.
\item \emph{Domain Expert}: vet AHP ranking and short list.
\item With short list:
\begin{enumerate}
\item Survey developers
\item Usability experiments
\item Performance benchmarks
\item Maintainability experiments
\end{enumerate}
\item Rank short list using XXXXXX \pmi{How will we use the above step to rank the short list?}
\item Compare shallow and deep measures and ranking.
\item Document answers for research questions.
\end{enumerate}

@@

\begin{enumerate}
\item Must have viewable source code.
\item Ideally have a git repository. \pmi{Not all of mine had this..}
\end{enumerate}
